The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-22 ms/ms.tex
Updates from Overleaf

Repeating our perturbations across the six forcing scenarios ensures that we can identify important parameters not just under present-day conditions, but also in the future. In the case of evaporation (ET), the parameters that control the increase in ET due to warming tend to be different from the parameters that control present-day ET (Figure \ref{fig:et}). 
ET response can differ significantly from the default case (i.e. stray from the orange line), even when ET is near the default under present-day conditions (i.e. within the shaded region).
Many of the new parameters that appear in the ET response parameter rankings govern plant acclimation to temperature. 
These parameters, while not especially influential on present-day ET, will be important in governing the trend in ET going forward.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/lai_biome.pdf}
\caption{The eight most influential parameters on leaf area index within the CTL2010 ensemble, globally and within three biomes.}
\label{fig:lai}
\end{figure}

The volume of data generated by a large PPE can be overwhelming - our full dataset exceeds 2TB.  Our diagnostics package, which operates on only a subset of output variables, generated 1720 figures (\url{https://webext.cgd.ucar.edu/I2000/PPEn11_OAAT}). In many cases we have found it easier to utilize interactive plotting utilities to toggle through the various parameters, output variables, and forcing scenarios (Figure \ref{fig:panel}). Interactive widgets are relatively easy to generate while performing data analysis, but more difficult to host online, hence the screenshot.

\begin{figure}[h]
\centering
\includegraphics[width=40pc]{../figs/deltmap_panel.pdf}
\caption{Screenshot of interactive diagnostic for exploring maps of parameter effects. In this case, the effect of medlynslope on runoff within the CTL2010 ensemble. Increasing medlynslope tends to increase transpiration and reduce runoff.}
\label{fig:panel}
\end{figure}

>>>>

Repeating our perturbations across the six forcing scenarios ensures that we can identify important parameters not just under present-day conditions, but also in the future. In the case of evaporation (ET), the parameters that control the increase in ET due to warming tend to be different from the parameters that control present-day ET (Figure \ref{fig:et}). 
ET response can differ significantly from the default case (i.e. stray from the orange line), even when ET is near the default under present-day conditions (i.e. within the shaded region).
All of the new parameters that appear in the ET response parameter rankings govern plant acclimation to temperature. 
These parameters, while not especially influential on present-day ET, are among the most important in governing the trend in ET going forward.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/lai_biome.pdf}
\caption{The eight most influential parameters on leaf area index within the control ensemble, globally and within three biomes.}
\label{fig:lai}
\end{figure}

The volume of data generated by a large PPE can be overwhelming - our full dataset exceeds 2TB.  Our diagnostics package, which operates on only a subset of output variables, generated 1720 figures (\url{https://webext.cgd.ucar.edu/I2000/PPEn11_OAAT}). In many cases we have found it easier to utilize interactive plotting utilities to toggle through the various parameters, output variables, and forcing scenarios (Figure \ref{fig:panel}). Interactive widgets are relatively easy to generate within a data analysis session, but more difficult to host online, hence the screenshot.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/deltmap_panel.pdf}
\caption{Screenshot of interactive diagnostic for exploring maps of parameter effects. In this case, the effect of medlynslope on runoff within the control ensemble. Increasing medlynslope tends to reduce runoff, but only in regions with sufficient vegetation activity.}
\label{fig:panel}
\end{figure}
